The trade-offs of sharing pollinators: pollination service is determined by the community context

### 2020-03-28 paper/cover-letter.Rnw
Update manuscript to fit format requirements of The American Naturalist

%-----------------------------------------------------------------------------%
% Letter class
\documentclass[12pt]{letter}
\usepackage{hyperref}
\usepackage[backend=bibtex,style=verbose,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{geometry}
\usepackage{setspace}
\geometry{textwidth=30em, textheight=47\baselineskip}
% Name of sender
\name{Fernando Cagua}
% Signature of sender
\signature{Fernando Cagua}
% Address of sender
\address
{
    Fernando Cagua\\
    \href{mailto:efc29@uclive.ac.nz}{efc29@uclive.ac.nz} \\
    +64 20 402 68153 \\
    University of Canterbury, \\
    New Zealand
}
\date{July 5, 2019}
%-----------------------------------------------------------------------------%
\begin{document}
% Name and address of receiver
\begin{letter}
{
    Editorial Office,\\
    Ecology
}
% Opening statement
\opening{Dear Editorial Team,}
% Letter body
\onehalfspacing
<<my-label, eval=TRUE, echo=FALSE>>=
drake::loadd(msc_title)
@

We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{Ecology}.

@@

Our work provides fundamental understanding of plant reproductive biology, while also \emph{calling for a shift in the way we think about pollination in community ecology}, particularly from a theoretical perspective.
In contrast to the predominant literature, our study provides compelling evidence that animal-mediated pollination is a fluid dance between competition and facilitation.
Some lessons might also apply to other biological complex systems where facilitation and competition might be at odds like plant-frugivore and plant-fungus interactions.
Thus, we believe that this manuscript will be interesting to the broad readership of \emph{Ecology}.

Lastly, please note that the data used in this manuscript have been previously published by one of the co-authors\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017}.
However, the enclosed work represents a novel contribution from all involved.

@@

\hfill
Fernando Cagua,

>>>>

%-----------------------------------------------------------------------------%
% Letter class
\documentclass[12pt]{letter}
\usepackage{hyperref}
\usepackage[backend=bibtex,style=verbose,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{geometry}
\usepackage{setspace}
\geometry{textwidth=30em, textheight=47\baselineskip}
% Name of sender
\name{Fernando Cagua}
% Signature of sender
\signature{Fernando Cagua}
% Address of sender
\address
{
    Fernando Cagua\\
    \href{mailto:efc29@uclive.ac.nz}{efc29@uclive.ac.nz} \\
    +64 20 402 68153 \\
    University of Canterbury, \\
    New Zealand
}
\date{March 28, 2020}
%-----------------------------------------------------------------------------%
\begin{document}
% Name and address of receiver
\begin{letter}
{
    Editorial Office,\\
    The American Naturalist
}
% Opening statement
\opening{Dear Editorial Team,}
% Letter body
\onehalfspacing
<<my-label, eval=TRUE, echo=FALSE>>=
drake::loadd(msc_title)
@

We are submitting the manuscript entitled ``\Sexpr{msc_title}'' to be considered for publication in \emph{The American Naturalist}.

@@

Our work provides fundamental understanding of plant reproductive biology, while also \emph{calling for a shift in the way we think about pollination in community ecology}, particularly from a theoretical perspective.
In contrast to the predominant literature, our study provides compelling evidence that animal-mediated pollination is a fluid dance between competition and facilitation.
Some lessons might also apply to other biological complex systems where facilitation and competition might be at odds like plant-frugivore and plant-fungus interactions.
Thus, we believe that this manuscript will be interesting to the readership of \emph{The American Naturalist}.

Please note that the data used in this manuscript have been previously published by one of the co-authors\autocite{marrero_effect_2014,marrero_agricultural_2016,marrero_exotic_2017}.
However, the enclosed work represents a novel contribution from all involved.
Lastly, we would like to bring to your attention that an earlier version of this manuscript has been published as a preprint\autocite{cagua_trade-offs_2019}.

@@

\hfill
Fernando Cagua

### 2020-03-28 paper/manuscript.Rmd
Update running head
Update manuscript to fit format requirements of The American Naturalist

---
title: "The trade-offs of sharing pollinators: pollination service is determined by the community context"
author: 
  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
  - "Hugo J. Marrero^2^ ([hugomarrero@gmail.com](hugomarrero@gmail.com))"
  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
bibliography: bibliography.bib
csl: ecology.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 12pt
geometry:
  - textwidth=6.5in
  - textheight=9in
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[S-]{supp-info}
  - \usepackage[export]{adjustbox}
  - \usepackage[nomarkers]{endfloat}
  - \usepackage{caption}
  - \captionsetup{labelsep=none,textformat=empty}
  - \usepackage{ragged2e}
editor_options: 
  chunk_output_type: console
---

@@

^1^ Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8041, New Zealand

^2^ Centro de Recursos Naturales Renovables de las Zonas Semiáridas, CONICET, Camino de la Carrindanga Km. 7, 8000 Bahía Blanca, Argentina

**Running head:** Competition/facilitation in pollination

<!-- **Article type:** Report. -->

<!-- **Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text. -->

@@

**Author for correspondence:** E. Fernando Cagua (+64 20 4026 8153).

@@

\RaggedRight

@@

# Acknowledgements

`r paste(drake::readd(acknowledgements), collapse = "")`

>>>>

---
title: "The trade-offs of sharing pollinators: pollination service is determined by the community context"
#author: 
#  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
#  - "Hugo J. Marrero^2^ ([hugomarrero@gmail.com](hugomarrero@gmail.com))"
#  - "Jason M. Tylianakis^1^ #([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
#  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
bibliography: bibliography.bib
csl: the-american-naturalist.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 12pt
geometry:
  - textwidth=6.5in
  - textheight=9in
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[S-]{supp-info}
  - \usepackage[export]{adjustbox}
#  - \usepackage[nomarkers]{endfloat}
#  - \usepackage{caption}
#  - \captionsetup{labelsep=none,textformat=empty}
#  - \usepackage{ragged2e}
editor_options: 
  chunk_output_type: console
---

@@

<!-- ^1^ Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8041, New Zealand -->

<!-- ^2^ Centro de Recursos Naturales Renovables de las Zonas Semiáridas, CONICET, Camino de la Carrindanga Km. 7, 8000 Bahía Blanca, Argentina -->

<!-- **Running head:** The trade-offs of sharing pollinators -->

**Manuscript type:** Article.

**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text.

@@

<!-- **Author for correspondence:** E. Fernando Cagua (+64 20 4026 8153). -->

@@

<!-- \RaggedRight -->

\clearpage

@@

<!-- # Acknowledgements -->

<!-- `r paste(drake::readd(acknowledgements), collapse = "")` -->
